---
title: "howTo"
author: "Gwenaël Gouérou"
date: "13 October 2015"
output: html_document
---

<br><br>
This is a test to deploy gh-pages

<br><br>  

## Simplified method :  

1. Create a repo on github, initialized it with a README.md and clone it to your local  
2. Encode your .Rmd file in UTF-8  
3. knit your html file, and if they were not yet in the repo, 
move those two files to your local repo.  
4. if your report is not called index.html but has a meaningful name, include an extra 
index.html file in the local repo :  

```{r index.html, eval=FALSE}
<!DOCTYPE HTML>  
<html>  
  <head>  
      <title>Title of the project</title>  
	 </head>  
	 <body>  
	    <p>please go <a href="http://YOURNAME.github.io/YOURREPO/YOURREPORT.html">here</a> to read the report.</p>  
	 </body>  
</html>  
```

YOURNAME should be the user name you have on github.  
YOURREPO should be the name of the repo.  
YOURREPORT should be the name of your report.  

5. update the README.md  
6. you do not need to include your knitr cache to the commit.  
7. avoid too fancy css or adding image not created by knitr if you want to use this method  
8. push everything to github  
git add -A / git commit -m "your message" / git push origin master  

9. create the gh-pages in the simplest possible way  

on your repo page (the main page of this repo, where the README is read), 
just under the orange bar, find the branch button. 
Click the down arrow to show the list of branches.   

There is probably just master and a box that says search or add branches. 
Go in the box and type gh-pages  
then add/create this branch  

Now wait it can take a few minutes to compile.   

Then go to this address (make the obvious changes before, as per the above indications) :   http://YOURNAME.github.io/YOURREPO/YOURREPORT.html  

If the name of either YOURNAME, YOURREPO, or YOURREPORT 
contain upper and lower cases, respect that.  

You should see your html page displayed nicely on the web.   

<br>  

## Examples of R code chunks :  

```{r}
summary(cars)
```

and with plots, for example:  

```{r, echo=FALSE}
plot(cars)
```

END  