---
title: "howTo"
author: "Gwenaël Gouérou"
date: "13 October 2015"
output: 
    html_document:
        toc: TRUE
---

<br><br>
This is a test to deploy gh-pages

<br><br>  

## Simplified method :  

1. Create a repo on github, initialized it with a README.md and clone it to your local  
2. Encode your .Rmd file in UTF-8  
3. knit your html file, and if they were not yet in the repo, 
move those two files to your local repo.  
4. if your report is not called index.html but has a meaningful name, include an extra 
index.html file in the local repo :  

```{r index.html, eval=FALSE}
<!DOCTYPE HTML>  
<html>  
  <head>  
      <title>Title of the project</title>  
	 </head>  
	 <body>  
	    <p>please go <a href="http://YOURNAME.github.io/YOURREPO/YOURREPORT.html">here</a> to read the report.</p>  
	 </body>  
</html>  
```

YOURNAME should be the user name you have on github.  
YOURREPO should be the name of the repo.  
YOURREPORT should be the name of your report.  

5. update the README.md  
6. you do not need to include your knitr cache to the commit.  
7. avoid too fancy css or adding image not created by knitr if you want to use this method  
8. push everything to github  
git add -A / git commit -m "your message" / git push origin master  

9. create the gh-pages in the simplest possible way  

on your repo page (the main page of this repo, where the README is read), 
just under the orange bar, find the branch button. 
Click the down arrow to show the list of branches.   

There is probably just master and a box that says search or add branches. 
Go in the box and type gh-pages  
then add/create this branch  

Now wait it can take a few minutes to compile.   

Then go to this address (make the obvious changes before, as per the above indications) :   http://YOURNAME.github.io/YOURREPO/YOURREPORT.html  

If the name of either YOURNAME, YOURREPO, or YOURREPORT 
contain upper and lower cases, respect that.  

You should see your html page displayed nicely on the web.   

<br>  

## to pull the gh-pages into your local  

```{r, eval=FALSE}
git pull origin gh-pages
```

## alternative version of point 9 : create the gh-pages from git  

Everything written above in points 1 to 8 still apply, 
this is an alternate version for point 9 only.  

you need to be in the repo you've created and cloned in your local.  

create the gh-pages :
```{r eval=FALSE}
git checkout -b gh-pages
```

push to gihtub :
```{r eval=FALSE}
git push origin gh-pages
```

switch back to master to continue working 
(no "-b" this time as that was for making a new branch)
```{r eval=FALSE}
git checkout master
```

<br>  

## Now to make some changes !!!

verify which branch you're in
```{r eval=FALSE}
git branch -v
```

You can decide to make changes first in either the master branch or gh-pages branch. 
That's fine, just be careful to make all the changes first in one branch before 
merging them. 

you made some changes in the repo. 
Note that you're not going to see the branches in the physical folder. 
Remember this is version control. In your physical folder you'll only 
see the latest file, in version control you can see earlier version.  

Let's assume you're working in the master branch.  

```{r eval=FALSE}
git status
git add -A           ## or whichever method you prefer/need at this moment, it can be git add index.html
git commit - m "message"
``` 

Then switch to the other branch, in this case gh-pages  
```{r eval=FALSE}
git checkout gh-pages
```

"pull" your changes from master  
```{r eval=FALSE}
git pull . master
```

the "." means your local repository (you could also "git merge master")  


You can see the new commit with :  
```{r eval=FALSE}
git log
```

Then, before forgetting, switch back to your master branch, 
so you can continue working and making even more changes  
```{r eval=FALSE}
git checkout master
```

Finally, push both branch to your github account :  

```{r eval=FALSE}
git push origin master
git push origin gh-pages
```

You'll need to enter your credential in between the two commands 
but you don't need to switch branch to push gh-pages.

You can go on github,com to see the changes, and on github.io to see your html displayed.
Note : you may need to wait a few minute for this one
(YOURNAME.github.io/YOURREPO/YOURREPORT.html) to be updated.  

For later usage, know that the gh-pages can be only a small piece of the master branch. 
I mean they don't necessarily need to be identical in bigger projects.  

<br>  

END  